Future challenges for Research Software Engineering

### 2025-08-15 future_challenges_for_RSEng.tex

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious.
Kim is currently designing the software service stack at the university.
She increasingly struggles to find compelling Open Source alternatives that enables them to keep complete control of their data
rather than relying on software and tools that are backed by large, foreign corporate entities.
So far, she still has the support of the university board, since it values strategic autonomy.
Kay had left academia to work in an industrial R\&D department because of a more reliable employment.
There he gained valuable experience working in an industrial setting.
However, he was very happy when an opportunity arose to work in a central
RSE department with an open-ended contract. Apart from his main responsibility
of developing and maintaining software for an affordable water monitoring system
used in the global south, he now also teaches undergraduates digital literacy.
\end{story}

>>>>

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious.
Kim is currently designing the software service stack at the university.
She increasingly struggles to find compelling Open Source alternatives that enables them to keep complete control of their data
rather than relying on software and tools that are backed by large corporate entities.
So far, she still has the support of the university board, since it values strategic autonomy.
Kay had left academia to work in an industrial R\&D department because of a more reliable employment.
There he gained valuable experience working in an industrial setting.
However, he was very happy when an opportunity arose to work in a central
RSE department with an open-ended contract. Apart from his main responsibility
of developing and maintaining software for an affordable water monitoring system
used in the global south, he now also teaches undergraduates digital literacy.
\end{story}
